Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-07 doc/JFLA2022/snippets/Schutte/Ex42c.tex
jfla: Recompile snippets

\begin{alectryon}
  % Generator: Alectryon
  \sep
  \begin{sentence}
    \begin{input}
      ~~\PY{n+nb}{assert}~\PY{o}{(}\PY{n}{Hlt}\PY{o}{:}~\PY{n}{omega}~\PY{o}{\PYZlt{}}~\PY{n}{phi0}~\PY{l+m+mi}{2}\PY{o}{)}~\PY{n+nb+bp}{by}~\nl
      ~~~~~~\PY{o}{(}\PY{n+nb}{rewrite}~\PY{n}{omega\PYZus{}eqn}\PY{o}{;}~\PY{n+nb}{apply}~\PY{n}{phi0\PYZus{}mono}\PY{o}{,}~\PY{n}{finite\PYZus{}mono}\PY{o}{;}\nl
      ~~~~~~~~\PY{n+nb}{auto~with}~\PY{n}{arith}\PY{o}{).}
    \end{input}
    \sep
    \begin{output}
      \begin{goals}
        \begin{goal}
          \begin{hyps}
            \hyp{HAP}{\PY{n}{In}~\PY{n}{AP}~\PY{o}{(}\PY{n}{phi0}~\PY{o}{(}\PY{n}{F}~\PY{l+m+mi}{2}\PY{o}{))}}
            \sep
            \hyp{Hlt}{\PY{n}{omega}~\PY{o}{\PYZlt{}}~\PY{n}{phi0}~\PY{o}{(}\PY{n}{F}~\PY{l+m+mi}{2}\PY{o}{)}}
          \end{hyps}
          \sep
          \infrule{}
          \sep
          \begin{conclusion}
            \PY{n}{omega}~\PY{o}{+}~\PY{n}{F}~\PY{l+m+mi}{42}~\PY{o}{\PYZlt{}}~\PY{n}{phi0}~\PY{o}{(}\PY{n}{F}~\PY{l+m+mi}{2}\PY{o}{)}
          \end{conclusion}
        \end{goal}
      \end{goals}
    \end{output}
  \end{sentence}
\end{alectryon}

>>>>

\begin{alectryon}
  % Generator: Alectryon
  \sep
  \begin{sentence}
    \begin{input}
      ~~\PY{n+nb}{assert}~\PY{o}{(}\PY{n}{Hlt}\PY{o}{:}~\PY{n}{omega}~\PY{o}{\PYZlt{}}~\PY{n}{omega}\PY{o}{\PYZca{}}\PY{l+m+mi}{2}\PY{o}{)}~\PY{n+nb+bp}{by}~\nl
      ~~~~~~\PY{o}{(}\PY{n+nb}{rewrite}~\PY{n}{omega\PYZus{}eqn}\PY{o}{;}~\PY{n+nb}{apply}~\PY{n}{phi0\PYZus{}mono}\PY{o}{,}~\PY{n}{finite\PYZus{}mono}\PY{o}{;}\nl
      ~~~~~~~~\PY{n+nb}{auto~with}~\PY{n}{arith}\PY{o}{).}
    \end{input}
    \sep
    \begin{output}
      \begin{goals}
        \begin{goal}
          \begin{hyps}
            \hyp{HAP}{\PY{n}{In}~\PY{n}{AP}~\PY{o}{(}\PY{n}{phi0}~\PY{o}{(}\PY{n}{F}~\PY{l+m+mi}{2}\PY{o}{))}}
            \sep
            \hyp{Hlt}{\PY{n}{omega}~\PY{o}{\PYZlt{}}~\PY{n}{phi0}~\PY{o}{(}\PY{n}{F}~\PY{l+m+mi}{2}\PY{o}{)}}
          \end{hyps}
          \sep
          \infrule{}
          \sep
          \begin{conclusion}
            \PY{n}{omega}~\PY{o}{+}~\PY{n}{F}~\PY{l+m+mi}{42}~\PY{o}{\PYZlt{}}~\PY{n}{phi0}~\PY{o}{(}\PY{n}{F}~\PY{l+m+mi}{2}\PY{o}{)}
          \end{conclusion}
        \end{goal}
      \end{goals}
    \end{output}
  \end{sentence}
\end{alectryon}
